Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2021-10-26 Methods-and-Results.tex
chi sq fix

In a final step we check whether during the interaction the core
situational need is a meaningful predictor even when taking other
fundamental psychological needs into account. We focus on the three
commonly considered self determination needs: competence, autonomy, and
relatedness. We find that the core need adds significantly above a model
with only the self determination theory needs (random slopes models;
\(\chi^2\)(6\textit{N} = 21) = 0.003). We find that next to relatedness
(\textit{b} = 0.10, \textit{t}(361) = 4.04, \textit{p} \textless{} .001,
\textit{95\%CI}{[}0.05, 0.14{]}), the core need explains the most
variance in outgroup attitudes after an outgroup contact (\textit{b} =
0.09, \textit{t}(361) = 2.23, \textit{p} = 0.026,
\textit{95\%CI}{[}0.02, 0.17{]}). When compared to the model with only
the SDT needs, the core need fulfillment flexibly takes on some of the
explained variance of all of the three fundamental needs and competence
and autonomy needs are non-significant (all \textit{b} \textless{} 0.05,
all \textit{p} \textgreater{} 0.544). For full results see Online
Supplementary Information B.

>>>>

In a final step we check whether during the interaction the core
situational need is a meaningful predictor even when taking other
fundamental psychological needs into account. We focus on the three
commonly considered self determination needs: competence, autonomy, and
relatedness. We find that the core need adds significantly above a model
with only the self determination theory needs (random slopes models;
\(\chi^2\)(6, \textit{N} = 21) \textit{p} = 0.003). We find that next to
relatedness (\textit{b} = 0.10, \textit{t}(361) = 4.04, \textit{p}
\textless{} .001, \textit{95\%CI}{[}0.05, 0.14{]}), the core need
explains the most variance in outgroup attitudes after an outgroup
contact (\textit{b} = 0.09, \textit{t}(361) = 2.23, \textit{p} = 0.026,
\textit{95\%CI}{[}0.02, 0.17{]}). When compared to the model with only
the SDT needs, the core need fulfillment flexibly takes on some of the
explained variance of all of the three fundamental needs and competence
and autonomy needs are non-significant (all \textit{b} \textless{} 0.05,
all \textit{p} \textgreater{} 0.544). For full results see Online
Supplementary Information B.
